% !TEX program = xelatex

\documentclass{resume}

\usepackage{tfrupee}

\usepackage{xcolor}
\usepackage[colorlinks = true,
            linkcolor = blue,
            urlcolor  = blue,
            citecolor = blue,
            anchorcolor = blue]{hyperref}

\newcommand{\MYhref}[3][blue]{\href{#2}{\color{#1}{#3}}}%

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Divya Raj}

\basicInfo{
  \email{divya21raj@gmail.com} \textperiodcentered\ 
  \MYhref{https://www.linkedin.com/in/divya21raj/}{\faLinkedin}
  \textperiodcentered\ 
  \MYhref{https://github.com/divya21raj}{\faGithub}
  \textperiodcentered\ 
  \MYhref{https://divya21raj.github.io/}{Website}
  }

\section{\faGraduationCap\ Education}

\datedsubsection{\textbf{Shiv Nadar University}, Greater Noida, Uttar Pradesh}{2016 -- 2020}
\textit{B.Tech} in Computer Science and Engineering - {CGPA} 8.62

\section{\faBriefcase\ Work Experience}

\datedsubsection{\textbf{Goldman Sachs}}{Jan 2020 -- Now}
\begin{itemize}
    \item Laid the foundation for adapting current data models to a new system we were developing. Made a Java library and various other scripts to automate the process for 100s of such models.
    \item Devised efficient algorithms and used the appropriate data structures to load and process large amounts of financial data on the client side. Used React to visualize it beautifully. 
\end{itemize}

\datedsubsection{\textbf{Dell}
\MYhref{https://docs.google.com/document/d/1BL8KUlzVYAUHJLVLFs3t5KK8GMXidGLd/edit?usp=sharing&ouid=106787197400761353588&rtpof=true&sd=true}{\faBook}}{May 2019 -- Jul 2019}
\begin{itemize}
    \item Worked with the Authentication team, providing the POC for a new service mesh based architecture.
    \item Set up the Istio service mesh over a cluster of micro-services and enabled service to service JWT authentication at the level of this mesh.
\end{itemize}

\datedsubsection{\textbf{Plabro} \MYhref{https://play.google.com/store/apps/details?id=com.plabro.realestate&hl=en_IN&gl=US}{\faAndroid}}{May 2018 -- Nov 2018}
\begin{itemize}
    \item Worked on their new Android application "Lookup", a real estate app that automatically picks up empty properties, and suggests them to buyers.
  \item Working with REST APIs, Chat SDK, Payment gateways integration, optimizing the current UI code-base.
\end{itemize}

\section{\faLaptop\ Projects \MYhref{https://github.com/divya21raj/}{\faGithub}}

\datedsubsection{\textbf{UniPool}
\MYhref{https://github.com/divya21raj/UniPool}{\faGithub} \MYhref{https://play.google.com/store/apps/details?id=garbagecollectors.com.unipool&hl=en}{\faAndroid}
\MYhref{https://www.youtube.com/watch?v=RJ32ujf2o64}{\faYoutube}
}{Nov 2017 -- Mar 2018}
An Android app providing a platform for students to find potential cab-poolers, which makes the cab more affordable for students, keeping in view that the university is located in a remote area. 
\begin{itemize}
    \item Used by around 1000 students on campus, was later integrated into the university's official app. Was also presented at Google I/O '18.
    \item Involved sensible UI/UX design, a chat implementation and handling overlapping transactions on Firebase.
\end{itemize}

\datedsubsection{\textbf{Actor Recognition In Movies} \MYhref{https://github.com/divya21raj/Actor-Recognition-In-Movies}{\faGithub}}{Dec 2019 -- May 2020}
Recognizing actors in a movie clip or image, by detecting the face in a particular frame and then comparing the face with a dataset of faces.
\begin{itemize}
  \item Face detection achieved by using either the CNN or HOG model.
  \item Efficient comparison of faces by using a binary search over a list of vectors, ensuring real-time results.
\end{itemize}

\datedsubsection{\textbf{Wiew} \MYhref{https://github.com/divya21raj/Wiew}{\faGithub}
\MYhref{https://www.linkedin.com/posts/divya21raj_2020-has-been-a-tough-year-for-everyone-activity-6761208104152551424-kQ5J}{\faLinkedin}}
{Nov 2020 -- Jan 2021}
\begin{itemize}
  \item A React web app to watch local and online videos in sync with your friends, while video calling them.
  \item Video calling done via Twilio, video syncing done with a custom clock sync algorithm, taking into account that the video can be paused and played by any party involved. 
\end{itemize}

\section{\faInfo\ Miscellaneous}
\begin{itemize}[parsep=0.5ex]
  \item Founding member of the Google Developer Student Club at my university. Conducted various technical lectures and workshops, mentored various student projects across the campus.
  \item Part of my University’s Dean’s List for three semesters.
  \item \youtube[divya21raj]{https://www.youtube.com/user/divya21raj} My youtube channel with 6K subscribers, generated a revenue of around \rupee~60K last year.
  \item Languages: \textbf{English} - Fluent, \textbf{Hindi} - Native speaker, \textbf{Korean, Spanish} - Competent
\end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
